### 2021-01-18 1.latex_manuscript/manuscript.tex
Changes
- Updated latex report with descriptives.
- Updated and added README files in subfolders.
- Created the `main analysis` folder.

%Title page 
\begin{titlepage}
\begin{center}
\LARGE{\textbf{The Realtime Assessment of Mental Workload by Means of Multiple Bio-Signals}}\\
\vspace*{2\baselineskip}
\Large{\textbf{Master thesis Report}}\\
Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
\vspace*{1\baselineskip}
Utrecht University\\
\vspace*{4\baselineskip}
{Bart-Jan Boverhof, 6000142}\\
\vspace*{1\baselineskip}
{\textbf{Thesis Supervisor}}\\
Prof.dr.ir. B.P. Veldkamp\\
\vspace*{1\baselineskip}
{\textbf{Date}}\\
January 7, 2021\\
\vspace*{1\baselineskip}
\end{center}
\end{titlepage}

@@

\subsubsection{Respondents}
In total, 25 respondents have participated in the study. No additional descriptive statistics can be presented in the this section as of yet. The respondents are students recruited from the University of Twente. Recruitment has been conducted by means of Sona, which is a cloud-based participant management system. A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker. This was assessed by means of a short demographic questionnaire prior to the experiment. Additionally, respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

@@

\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\bigskip
\caption{Sampling Rate per Modality}
\label{table:samplingrate}
\begin{tabular}{ll}
    & Specified sampling rate (Hz) \\ \hline
 Electroencephalogram (EEG) & 200                         \\
Galvanic Skin Response (GSR) & 5                           \\
Photoplethysmography (PPG) & 100                         \\ \hline
\end{tabular}
\end{table}
\bigskip
\egroup

>>>>

%Title page 
\begin{titlepage}
\begin{center}
\LARGE{\textbf{The Realtime Assessment of Mental Workload by Means of Multiple Bio-Signals}}\\
\vspace*{2\baselineskip}
\Large{\textbf{Masterthesis Report}}\\
Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
\vspace*{1\baselineskip}
Utrecht University\\
\vspace*{4\baselineskip}
{Bart-Jan Boverhof, 6000142}\\
\vspace*{1\baselineskip}
{\textbf{Thesis Supervisor}}\\
Prof.dr.ir. B.P. Veldkamp\\
\vspace*{1\baselineskip}
{\textbf{Date}}\\
January 7, 2021\\
\vspace*{1\baselineskip}
\end{center}
\end{titlepage}

@@

\subsubsection{Respondents}
In total, 25 respondents have participated in the study. Demographic information of the respondents is set forth in Table \ref{table:demographics}. The respondents are students recruited from the University of Twente. Recruitment has been conducted by means of Sona, which is a cloud-based participant management system. A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker. This was assessed by means of a short demographic questionnaire prior to the experiment. Additionally, respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

\bgroup
\def\arraystretch{1.6}  
\begin{table}[h]
\bigskip
\caption{Demographic Overview Respondents}
\label{table:demographics}
\begin{tabular}{rrrr}
  \hline
 & Female & Male \\ 
  \hline
10-19 &   7 &   0 &  \hspace{1cm} \\ 
  20-29 &  13 &   4 &   \\ 
  30-39 &   1 &   1  &   \\ 
  40-49 &   0 &   8  &   \\ 
  50-59 &   0 &   0 &   \\ 
  60-69 &   0 &   4 &   \\ 
   \hline
   \bigskip
\end{tabular}
\end{table}
\egroup

@@

\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\bigskip
\caption{Sampling Rate per Modality}
\label{table:samplingrate}
\begin{tabular}{ll}
    & Specified sampling rate (Hz) \\ \hline
 Electroencephalogram (EEG) & 200                         \\
Galvanic Skin Response (GSR) & 5                           \\
Photoplethysmography (PPG) & 100                         \\ \hline
   \bigskip
\end{tabular}
\end{table}
\egroup
